Augmenting the DonorsChoose.org Corpus for Meta-Learning

### 2019-05-06 doc/poster/main.tex
poster/main.tex: Drop an unimportant reference
{paper,poster}/main.tex: Fix spelling and grammar

				Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way. We are augmenting a public domain dataset intrinsically about recommendations which to our best knowledge has not been used for meta-learning before in the scientific community. Yet due to its feature-rich and vast corpus is suitable.
			\end{block}
		\end{column}

@@

						\begin{figure}[ht]
							\centering
							\subcaptionbox{Statistics\label{fig:MetaLearnerStatistics}}{
								\includegraphics[width=.45\textwidth,height=\textheight,keepaspectratio]{{{../res/learning_subsystem_position}}}
							}
							\hspace{.5em}
							\subcaptionbox{Perfromance\label{fig:MetaLearnerPerformance}}{
								\includegraphics[width=.45\textwidth,height=\textheight,keepaspectratio]{{{../res/meta_learner_performance_average_position}}}
							}
							\caption{Statistical features of the recall-positions of the learning subsystem are shown in~\subref{fig:MetaLearnerStatistics}. The dashed green lines indicate the means, the straight orange lines the medians. The percentage below each algorithm indicates how often it is the best possible algorithm. To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.
							The performance of the meta-learner system is shown in~\subref{fig:MetaLearnerPerformance}. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}%
							\label{fig:MetaLearner}
						\end{figure}
					\end{column}
				\end{columns}
			\end{block}
		\end{column}
	\end{columns}

>>>>

				Our objective is to address the data augmentation part in a comprehensive and reproducible way. We are augmenting a public domain dataset intrinsically about recommendations which to our best knowledge has not been used for meta-learning before in the scientific community. Yet due to its feature-rich and vast corpus it is suitable.
			\end{block}
		\end{column}

@@

						\begin{figure}[ht]
							\centering
							\subcaptionbox{Statistics\label{fig:MetaLearnerStatistics}}{
								\includegraphics[width=.45\textwidth,height=\textheight,keepaspectratio]{{{../res/learning_subsystem_position}}}
							}
							\hspace{.5em}
							\subcaptionbox{Performance\label{fig:MetaLearnerPerformance}}{
								\includegraphics[width=.45\textwidth,height=\textheight,keepaspectratio]{{{../res/meta_learner_performance_average_position}}}
							}
							\caption{Statistical features of the recall-positions of the learning subsystem are shown in~\subref{fig:MetaLearnerStatistics}. The dashed green lines indicate the means, the straight orange lines the medians. The percentage below each algorithm indicates how often it is the best possible algorithm. To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.
							The performance of the meta-learner system is shown in~\subref{fig:MetaLearnerPerformance}. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}%
							\label{fig:MetaLearner}
						\end{figure}
					\end{column}
				\end{columns}
			\end{block}
		\end{column}
	\end{columns}
